Convex Surrogates via Polyhedral Losses

### 2019-04-29 neurips-19/cvx-fin.tex
finish outline

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
(A generic loss will also be written $L$.)
We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

@@

\begin{itemize}
\item Def: ``discrete loss'' should connote some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.
\item Prop: $L$ embeds discrete $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  \\
  {\tiny Proof: use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
\item Note: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.  In contrast, we focus exclusively on non-strictly-convex risks.
\item Prop: $L$ embeds a discrete loss iff $\risk{L}$ is polyhedral.
  \\
  {\tiny Proof: just take the discrete reports to be the facets, and use the Bayes risk result.}
\item Prop: If $L$ is polyhedral, then so is $\risk{L}$.
  \\
  {\tiny Proof: not sure if this is trivial or not, but it sure follows from what we know.}
\item Cor: Every polyhedral loss embeds a discrete loss.
\item Converse via DKR construction: every discrete $\ell$ is embeddable.
    \\
  {\tiny Proof: already have it.}
\item Corollary: our current Theorem~\ref{thm:finite-elicit-embed}.
\item Prop: ``separated'' link implies blah blah ERM.  (Modify Arpit--Shivani Theorem 3, since it's not quite general enough.)
\item Theorem: If $L$ is polyhedral and embeds $\ell$, there is a separated link.  (TO PROVE)
\item Note: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just study elicitation complexity and not worry about how fancy the link is (calibrated vs separated).
\item Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never opetimal.  This theorem would then not need the ``polyhedral'' part.
\end{itemize}

>>>>

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
(A generic loss be written $L:\R\to\reals^\Y$.)
We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y$ is the function $\risk{L}:\Delta(\Y)\to\reals$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$; naturally for discrete losses we will write $\risk{\ell}$.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

@@

\begin{itemize}
\item Prop: $L$ embeds discrete $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  \raft{Note: ``discrete loss'' now connotes some regularity as well, just like we did with finite properties: every report should correspond to a full-dimensional cell.}
  \raft{Note: DKR (section 3.1) realized the importance of matching Bayes risks, but they could only give general results for strictly convex (concave I should say) risks, in part because they fixed the link function to be a generalization of $\sgn$.  In contrast, we focus exclusively on non-strictly-convex risks.}
  \\
  {\tiny Proof: use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
\item Prop: $L$ embeds a discrete loss iff $\risk{L}$ is polyhedral.
  \\
  {\tiny Proof: just take the discrete reports to be the facets, and use the Bayes risk result.}
\item Prop: If $L$ is polyhedral, then so is $\risk{L}$.
  \\
  {\tiny Proof: not sure if this is trivial or not, but it sure follows from what we know.}
\item Cor: Every polyhedral loss embeds a discrete loss.
\item Prop: Every discrete $\ell$ is embedded by a polyhedral loss.
    \\
  {\tiny Proof: already have it (DKR construction).}
\item Cor: For a finite $\gamma$, elicitable iff embeddable iff embeddable via polyhedral loss (Theorem~\ref{thm:finite-elicit-embed}).
\item \raf{What else do we want to say about properties?  Prop~\ref{prop:embed-trim}?}
\end{itemize}

New section(?)

\begin{itemize}
\item Prop: Separated link implies consistency.
  \\
  {\tiny Proof: Use Hari's Theorem 8.1-8.3.}
\item Theorem: If $L$ is polyhedral and embeds $\ell$, there is a separated link.  (TO PROVE)
  \raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.  This theorem would then not need the ``polyhedral'' part.}
\item Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.  \raf{Is this true?}
\end{itemize}

Finally, here's a proposal for how to restate the 1d stuff.

\begin{itemize}
\item Def: order-sensitive, orderable.
\item Theorem (Lambert et al): $\ell$ order-sensitive iff $\prop{\ell}$ orderable.
\item Theorem: $\ell$ 1-embeddable iff $\ell$ 1-embeddable via polyhedral loss iff $\ell$ order-sensitive.
% \item Prop: Every polyhedral $L:\reals\to\reals^\Y$ embeds an order-sensitive $\ell$.
\item Prop: If convex $L:\reals\to\reals^\Y$ indirectly elicits finite $\gamma$, then $\gamma$ is orderable.
\item Theorem: TFAE for all the complexity classes.
\end{itemize}
